---
title: "R-package rtmle: user cases"
author: "Alessandra Meddis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Examples Treatment combinations (draft 1)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## About

The **R**-package rtmle implements a class of targeted minimum loss estimators for the analysis of longitudinal register data. 
We specify the different scenarios this package can be used for:

```{r echo=FALSE}
cat("
|--------------|-----------|---------|-----------|
| Intervention |Exposure(s)| Outcome | Available |
|--------------|-----------|---------|-----------|
| Static       |one Binary |   B-S   | Yes       |
| Dynamic      |one Binary |   B-S   | Yes       |
| Stochastic   |one Binary |   B-S   | Yes       |
|--------------|-----------|---------|-----------|
| Static       | one Categ |   B-S   | soon      |
| Dynamic      | one Categ |   B-S   | soon      |
| Stochastic   | one Categ |   B-S   | soon      |
|--------------|-----------|---------|-----------|
| Static       | two Binary|   B-S   | soon      |
| Dynamic      | two Binary|   B-S   | soon      |
| Stochastic   | two Binary|   B-S   | soon      |
|--------------|-----------|---------|-----------|
| Static       | two Categ |   B-S   | No        |
| Dynamic      | two Categ |   B-S   | No        |
| Stochastic   | two Categ |   B-S   | No        |
|--------------|-----------|---------|-----------|
| Static       | continuous|   B-S   | No        |
| Dynamic      | continuous|   B-S   | No        |
| Stochastic   | continuous|   B-S   | No        |
|--------------|-----------|---------|-----------|
", sep="n")
```

## Defining the protocol

The function *protocol* is needed as first step to define the type of intervention of interest.
Here we specify:

 - *name* : name of the protocol 
 - *treatment_variables*:  name(s) of the variable(s) that the protocols intervenes upon
 - *intervention*: the values of the treatment(s) the variables are set to under the intervention.
 If two treatments this would be either a list or a matrix. 
 In case of stochastic or dynamic intervention, a function needs to be specified.
 

### Examples: 

#### Static Intervention: one Binary exposure (Always treated protocol)

```{r}
protocol(x) <- list(name = "always A",treatment_variables = "A",
intervention = 1)
```

OR 

```{r}
protocol(x) <- list(name = "always A",treatment_variables = c("A_1","A_2","A_3"),
intervention = 1)
```


OR 

```{r}
protocol(x) <- list(name = "always A",treatment_variables = c("A_1","A_2","A_3"),
intervention = c(1,1,1))
```

#### Static Intervention: two Binary exposures (A,B)

```{r}
protocol(x) <- list(name = "always combined",treatment_variables = list("A"=c("A_1","A_2","A_3"),"B"=c("B_1","B_2","B_3")),
intervention = list("A"=c(1,1,1),"B"=c(1,1,1)))
```

OR

```{r}
protocol(x) <- list(name = "always combined",treatment_variables = matrix(c("A_1","A_2","A_3", "B_1","B_2","B_3"),3),
intervention = matrix(rep(1,6),3))
```

OR

```{r}
protocol(x) <- list(name = "always combined", treatment_variables = c("A","B"),
intervention = c(1,1))
```


